---
title: "Assignment 1: Introduction to Probability"
author: "Ben Arancibia"
date: "February 4, 2015"
output: pdf_document
---

__**Dobrow Chapter 1**__

**1.6**

(a) {X + Y = 4} solution: {13, 22, 31}

(b) {X + Y = 9} solution: {45, 36, 63, 54}

(c) {Y = 3} solution (assuming that X value does not matter): {13, 23, 33, 43, 53, 63}

(d) {X = Y} solution: {11, 22, 33, 44, 55, 66}

(e) {X > 2Y} solution: {31, 52}

**1.8**

If a couple plans on having children until they have 1 girl or 6 boys, the sample space or  $\Omega$ would be the following (G = Girl, B = Boy):

{G}

{BG}

{BBG}

{BBBG}

{BBBBG}

{BBBBBG}

{BBBBBB}

A reasonable random variable for having a girl is 0.5, P(G) = 0.5. The same probability can be associated with a boy, P(B) = 0.5. This random variable was selected because the outcomes of gender is 1 of 2 possbilities.

**1.10**

In order for the random experiment with three possible outcomes a, b, and c, with P(a) = p, P(b) = p^2, and P(c) = p then the three probailities when added together must = 1. 

A possible probability for the p = 27/64. 

**1.16**

A license plate can be two, three, four, or five letters long and taken from the alphabets A to Z. All letters are possible, including repeats.

(A) The probability of the plate A-R-R is:

$(1/26) * (1/26) * (1/26) * (1/4)$ = 0.00001422394

The 1/4 is also multipled because the plate probability has to be taken into account. There is a .25 percentage chance that the three letter plate is chosen. 

(B) The probability that the four letter plate is chosen is 1/4 or .25. The reason for this is that there are four types of lengths for license plates that can be chosen.

(C) Probability of a plate being a palindrome depends on the exact requirements of the palindrome. If looking for a three letter plate and a palindrome such as DAD, the probability could be as follows:

$(1/26) * (1/26) * (1/26) * (1/4)$ = 0.00001422394

(1/4) = selecting the correct plate
(1/26) = chances of selecting letters

If looking for a four letter plate and palindrome such as CIVIC, the probability would be as follows:

$(1/4)  *(1/26) * (1/26) * (1/26) * (1/26)$ = 0.0000005470

(D) The probability of the plate having one R is 1/26 no matter the type of plate being selected.

**1.22**

$P(AUB)$ = 0.6 and $P(AUB^c)$=0.8

$P(AUB^c)$ = [1-$P(AUB)$] + $P(A)$

0.8 = [1 - 0.6] + $P(A)$

0.8 = 0.4 + $P(A)$

$P(A)$ = 0.4

**1.37**

Random Integer between 1 and 5000 divisible by 4,7,10

$P(D4UD7UD10)$ = $P(D4)$ + $P(D7)$ + $P(D10)$ - $P(D4D7)$ - $P(D4D10)$ - $P(D7D10)$ + $P(D4D7D10)$

$P(D4)$ = [5000/4]/5000
$P(D7)$ = [5000/7]/5000
$P(D10)$ = [5000/10]/5000
$P(D4D7)$ = [5000/28]/5000
$P(D4D10)$ = [5000/40]/5000
$P(D7D10)$ = [5000/70]/5000
$P(D4D7D10)$ = [5000/280]/5000


$P(D4UD7UD10)$ = 0.40

**1.44**

```{r}
require(dice)
```

```{r}
getEventProb(nrolls = 5,
             ndicePerRoll = 1,
             nsidesPerDie = 4,
             eventList = list(2))

```

**1.45**


