---
title: "Assignment 2"
author: "Ben Arancibia"
date: "February 17, 2015"
output: pdf_document
---

__**Dobrow Chapter 3**__

**3.3**

If a tree has 70% change of being infected with root rot or bark disease there is a 40% chance it has root disease. If you take the compliment of 40%, (1-.4), then the infected tree has a 60% (.6) that it is bark disease. 

P(Infected|Bark) = (.7) * (.6)
P(I|B) = 0.42

**3.6**

Lottery tickets 1 and 1000
Tickets needed to buy to get probability of winning 50%

x=tickets needed to get probability of winning to 50%

.5=(1/1000)*x
x=500 Tickets

**3.8**
50-50 chance that the queen carries hemophilia and each prince has 50-50 change of having hemophilia.

a) three princes without the disease, what the is the probability the queen is a carrier.

P(H|E) = P(H)P(E|H)/P(H)P(E|H + P(H^C)P(E|H^C)
.5^3 * .5 / (.5^3 * .5 + .5)

=.111

b) If there is a four prince what is the probability
P(H|E) = P(H)P(E|H)/P(H)P(E|H + P(H^C)P(E|H^C)
.5^4 * .5 / (.5^4 * .5 + .5)

=0.05882353

**3.16**

$(n/k)$ = $n!/k!(n-k)!$

a) Straight Flush (5 cards same suit)
P(Straight Flush) = 36/(52/5)
P(Straight Flush) = $36/(8.065818e+67/(120*2.586232e+59))$
=1.385169e-05

b) Four of a Kind (four cards one face value and one other card)
P(Four of a Kind) = 624/(52/5)
=$624/(8.065818e+67/(120*2.586232e+59))$
=0.000240096

c) Full House (three cards of one face value and wo of another face value)
P(Full House) = 3744/(52/5)
=$3744/(8.065818e+67/(120*2.586232e+59))$
= 0.001440576

d) Flush (five cards same suit)
P(Flush) = 5108/(52/5)
=$5108/(8.065818e+67/(120*2.586232e+59))$
= 0.001965401

e) Straight (Five cards in a sequence)
P(Straight) = 10200/(52/5)
=$10200/(8.065818e+67/(120*2.586232e+59))$
= 0.003924646

f) Three of a Kind (Three cards)
P(Three Kind) = 54912/(52/5)
=$54192/(8.065818e+67/(120*2.586232e+59))$
= 0.02085141

g) Two Pair
P(Two Pair) = 123552/(52/5)
=$123552/(8.065818e+67/(120*2.586232e+59))$
= 0.04753901

h) One Pair
P(One Pair) = 1098240/(52/5)
=$1098240/(8.065818e+67/(120*2.586232e+59))$
= 0.4225689

**3.22**
```{r}
p <- as.numeric(1/6)
scenarios <- c(1, 2, 3)
 
for (i in scenarios) {
  # Accumulate the probability that fewer than the target # of sixes occurs.
   x <- 0
   # Total number of dice.
   n <- 6 * i
   # Calculate the probability for each possible # of sixes that is less than the goal.
   for (j in 0:(i-1)) {
     x <- x + dbinom(j, n, p)
   }
   print(paste("Probability of at least", i, "six in", n, "fair dice:", 1 - x))
}
```


**3.26**

a) Find the Probability of zero detections

a = occupancy rate
p = detection rate
n = number of sites

Assume n = 1000 and occupancy rate = 0.25, detection rate

```{r}
dbinom(0, 1000, .25)

```

Based on these assumptions, 0.05 is the answer. More information is needed to determine chance for 0 detection rate. The question is very vague though

b)

The Probability function for Z is 

P(Z) = 1 - P(Z<5) = 1 - $Sigma$ P(Z=k)
1- $Sigma$$(5 / k)$ (.5)^k(.5)5-k


n = 5
p = .5
a = 0.75

**3.34**
Over 104 seasons there were there were 206 no hitter games. That means the rate of no hitters is 206 per 104 years. $\lambda$ = 206/104. 206/104 = 1.98

```{r}
probs <- dpois(0:7, 1.98)
probs <- c(probs, 1-ppois(7, 1.98))
games <- 104*probs
knitr::kable(games)
```

The table goes from 0 games to 7 games and the expected seasons per game. So 14.35 is the expected number of seasons with 0 no hitters, 28.43 seasons with 1 no hitter, etc.


**3.45**
```{r}

probs <- dpois(0:4, 0.61)
probs <- c(probs, 1-ppois(4, 0.61))
expected <- 200*probs
expected
barplot(expected)

probs2 <- dpois(0:4, 0.61)
probs2 <- c(probs2, 1-ppois(4, 0.61))
expected2 <- 10000*probs2
expected2
barplot(expected2)

```


__**Dobrow Chapter 4**__

**4.6**
E[$X^2$]=1, E[$Y^2$]=2, and E[XY]=3

E[$(X+Y)^2$] = E[$(X^2 + 2XY + Y^2)$]

E[$1^2 + 2(3) + 2^2$]

E[1+6+4]

E[11]

**4.16**

If X and Y are independent random variables E[X/Y] = E[X]/E[Y]. 

Proof
Let X and Y be indepdent random variables then any function f and g, 

$E[f(X)/g(Y)] = E[f(X)]/E[g(Y)]$.

Let f and g be the identify function gives
$E[X/Y] = E[X]/E[Y]$

