---
title: 'IS 606: Statistics and Probability for Data Analytics Final Exam'
author: "Ben Arancibia"
date: "May 22, 2015"
output: pdf_document
---

#Binomial or Hypergeometric

1) Binomial distribution to calculate the probability that there will be three success out of ten trials, probability of success is 0.30

```{r}
dbinom(3, 10, 0.3) #dbinom(k, n, p)
```

2) Expected value and the standard deviation for binomial experiment with ten trials and P = 0.30

Expected value = mean

n*p = expected value

```{r}
10*.30
```

Standard deviation is sqrt of variance.

```{r}
sqrt(10*.3*(1-.3)) 
```

3) Hypergeometric distribution to calculate the probability that there will be three success out of ten trials, n = 20 with eight possible successes. 

```{r}
dhyper(3, 8, 12, 10) #dhyper(x, success, n-sucess, trials) (x,m,n,k)
```

4) Expected value and the standard deviation for a hypergeometric experiment with ten trials, n=20 with eight possible successes

Expected value = n*(k/ N)

```{r}
10*(8/20)
```

Standard deviation

```{r}
sqrt(10*(8/20)*(1-(8/20))*((20-10)/(20-1)))
```

5) hypergeometric distribution to calculate the probability that there will be three success out of ten trials, N=60 with 24 possible successes.

```{r}
dhyper(3, 24, 36, 10)
```

6) Expected value and the Standard deviation for a hypergeometric experiment with ten trials, N=60 with 24 possible successes

Expected value = n*(k/ N)
```{r}
10*(24/36)
```

Standard deviation

```{r}
sqrt(10*(24/60)*(1-(24/60))*((60-20)/(60-1)))
```

7) What population size does the binomial start to make a strong approximation for the hypergeometric distribution?

The Hypergeometric(n, D, M) can be approximated by Binomial(n, D/M). The approximate works well when n < 0.1 M

As long as n is less 0.1 of success trials

#Conditional Probability and the Naive Bayes Classification Method


