---
title: "Assignment 3 - More on Random Variables"
author: "Ben Arancibia"
date: "March 11, 2015"
output: pdf_document
---
__**Chapter 4**__

**4.24**

Find the variance of a fair die roll.

To find variance first you need to find the expected value: 

Expected Value: 
(1 * 1/6) + (2 * 1/6) + (3 * 1/6) + (4 * 1/6) + (5 * 1/6) + (6 * 1/6) = 21/6 = 3.5

then take the variance of the expected value:

(1 - 3.5)^2 * 1/6 + (2 - 3.5)^2 * 1/6 + (3 - 3.5)^2 * 1/6  + (4 - 3.5)^2 * 1/6 + (5 - 3.5)^2 * 1/6 + (6 - 3.5)^2 * 1/6
= 70/24 
= 2.91


**4.36**

Cor(X,Y) = -0.5
Find V[X+Y]

V[X+Y] = V[X] + V[Y] + 2 COR(X,Y)

V[X] + V[Y] + 2 * (-0.5)

V[X+Y] = variance since it is equal distribution, mean, STD, variance are all the same.
=.25

**4.40**

E[X] = 1
E[X^2] = 2
E[X^3] = 5
E[X^15] = 15

E[Y] = 2
E[Y^2] = 6 
E[Y^3] = 22
E[Y^4] = 94

V[3X^2 - Y] = 138
V[X^2] = (9*(2)^4 - 2^2)
V[Y] = 6 - 4

E[X^4Y^4]
15*94
=1410

COV(X, X2)
V[X^2] = 9 - 2^2
V[X] = 1 - 1
6 - 3
=3

V[X^2Y^2]
V[X^2] = 6
V[Y^2]1296-36
6+1260
=1266


**4.56**
```{r}
sim <- sample(c(-10,-10,-10,0,0,14), 100000, replace = T)
mean(sim)
var(sim)

```

**4.58**

```{r}
x <- rpois(100000, 1)
y <- rpois(100000, 2)
var(3*x^2 - y)
mean(x^4 * y^4)
cov(x, x^2)
var(x^2*y^2)

```


__**Chapter 5**__

**5.4**
.01% chance of being defective

a) Find the probability that exactly 110 Components produced before defective one:
P(X=k) = (1-p)^k-1
((1-.01)^109)*.01
=0.0033

b) Find the probability that takes at least 110 components before defective:
P(X>110)
(1-p)^k
((1-.01)^109)
=0.33

c) Find is the expected number of components that will be produced before a defective one:
E[X] = 1/p
1/.01
=100

**5.12**

X ~ NgBin(R,p)
p=0.5

2 (k -1 | 3) (1/2)^k

E[X] = 4(0.125) + 5(0.25) + 6(0.3125) + 7(0.3125)
=5.8125

**5.20**
500 deer, sample of 50 deer caught and tagged.

20 are then caught.

a)
50/500
0.1*20
E[X] = 2

variance of E[X] = 1.8496

SD[X] = (1.8495)^1/2

=1.316

b)

P(X>=3) = (20 | 3) (480 | 17) / (500 | 20)

P(X>=3) = 0.322

**5.28**

10 rolls fair die, X = number of fives rolled, Y = number of even numbers, Z = number of odd numbers

a) COV(X, Y)

-nP(x)P(y)
-1/6 , 3/6
=-5/6

b) Cov(X, Z)
-nP(X)P(Z)*-1 #but if a 5 is rolled that is both odd number and a 5
1/6, 3/6, *-1

=5/6

**5.32**

Let X be the number of days when there is no homework. N = 42, p = 1/30, condition is prime number (1/15)
10 prime numbers

(1/30) * 42 (N) * 10 (prime numbers)

Number days expect to have no homework is 14

**5.34**

This is a hypergeometric distribution

Let X be 3 winners. N = 30 and six are winners

6/30
0.2*10
E[X]=2

P(X=3) = (10 | 3) (20 | 17) / (30 | 6)

P(X=3) = 0.23

**5.36**
```{r}
coupon <- function(n){
  i <- 0
  j <- 1
  a = vector(length=n)
  a[j] <- sample(1:n,1)
  remaining <- c(1:n)[-which(c(1:n) == a[j])]
  repeat
    {
      pick <- sample(remaining,1)
      i <- (i+1)
      if(any(pick == a))
        {
        next
        }
      else
        {
          j <- (j+1)
          a[j] <- pick
          }
      if(j == n)
        {
        break
        }
      }
  return(i)
  }

```

```{r}
mean(replicate(100000,coupon(10)))
sd(replicate(100000,coupon(10)))
```

**5.39**

```{r}
wins <- loss <- 0
successprob <- 0.25
series <- function(){
  gamecount <- 0
  while (wins < 4 && loss < 4){
    w <- rbinom(1,1,successprob)
    wins <- wins + w
    loss <- loss + 1 -w
  
  }
  wins + loss
}

mean(replicate(100000, series()))

sd(replicate(100000, series()))

```











